qcircuit 2.5.3 Tutorial

### 2017-11-30 CO681-QuantumInformationProcessing/assignments/assignment_05.tex
Problem 1

\begin{document}
\section{}
\subsection{a}
\paragraph{}
We have
\begin{align*}
\ket{\phi^+} &= \ket{00} + \ket{11}\\
\ket{\phi^-} &= \ket{00} - \ket{11} \\
\ket{\psi^+} &= \ket{10} + \ket{01} \\
\ket{\psi^-} &= \ket{10} - \ket{01}
\end{align*}
So then
$$\ket{\phi^+}\bra{\phi^+} + \ket{\phi^-}\bra{\phi^-} + \ket{\psi^+}\bra{\psi^-} = \begin{bmatrix}
1 & 0 & 0 &0 \\
0 & 1 & 1 & 0 \\
0 & 1 & 1 & 0 \\
0 &0 &0 &1
\end{bmatrix}$$
and 
$$\ket{\psi^-}\bra{\psi^-} = \begin{bmatrix}
0 & 0 &0 & 0\\
0 & 1 & -1 & 0 \\
0 & -1 & 1 & 0 \\
0 &0 &0 &0
\end{bmatrix}$$
Hence our Werner state $\rho$ as a $4\times 4$ matrix is
$$\rho = \begin{bmatrix}
\frac{1-p}{3} & 0 & 0 &0 \\
0 & \frac{1+2p}{3} & \frac{1-4p}{3} & 0 \\
0 & \frac{1-4p}{3} & \frac{1+2p}{3} & 0 \\
0 & 0 & 0 & \frac{1-p}{3}
\end{bmatrix}$$
The partial transpose of $\rho$ is 
$$(I \otimes T)\rho = \begin{bmatrix}
\frac{1-p}{3} & 0 & 0 &\frac{1-4p}{3} \\
0 & \frac{1+2p}{3} & 0 & 0 \\
0 & 0 & \frac{1+2p}{3} & 0 \\
\frac{1-4p}{3} & 0 & 0 & \frac{1-p}{3}
\end{bmatrix}$$
\end{document}

>>>>

\begin{document}
\section{}
\subsection{a}
\paragraph{}
We have (leaving off normalization)
\begin{align*}
\ket{\phi^+} &= \ket{00} + \ket{11}\\
\ket{\phi^-} &= \ket{00} - \ket{11} \\
\ket{\psi^+} &= \ket{10} + \ket{01} \\
\ket{\psi^-} &= \ket{10} - \ket{01}
\end{align*}
So then
$$\ket{\phi^+}\bra{\phi^+} + \ket{\phi^-}\bra{\phi^-} + \ket{\psi^+}\bra{\psi^-} = \frac{1}{2}\begin{bmatrix}
2 & 0 & 0 &0 \\
0 & 1 & 1 & 0 \\
0 & 1 & 1 & 0 \\
0 &0 &0 &2
\end{bmatrix}$$
and 
$$\ket{\psi^-}\bra{\psi^-} =\frac{1}{2} \begin{bmatrix}
0 & 0 &0 & 0\\
0 & 1 & -1 & 0 \\
0 & -1 & 1 & 0 \\
0 &0 &0 &0
\end{bmatrix}$$
Hence our Werner state $\rho$ as a $4\times 4$ matrix is
$$\rho = \frac{1}{6}\begin{bmatrix}
2(1-p) & 0 & 0 &0 \\
0 & 1+2p & 1-4p & 0 \\
0 & 1-4p & 1+2p & 0 \\
0 & 0 & 0 & 2(1-p)
\end{bmatrix}$$
The partial transpose of $\rho$ is 
$$(I \otimes T)\rho = \frac{1}{6}\begin{bmatrix}
2(1-p) & 0 & 0 &1-4p \\
0 & 1+2p3 & 0 & 0 \\
0 & 0 & 1+2p & 0 \\
1-4p & 0 & 0 & 1-3p
\end{bmatrix}$$
\subsection{b}
The eigenvalues $(I \otimes T)\rho$ are $\frac{1+2p}{6}$, $0$, $0$, and $\frac{3-6p}{6} = \frac{1-2p}{2}$. The least of which is $\frac{1-2p}{2}$. From our slides we know that $\rho$ is separable if and only if $(I \otimes T)\rho$ is positive semidefinite. This happens if and only if $\frac{1-2p}{2} \geq 0$, that is when $p \leq 1/2$.
\end{document}
